---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```


![stability-wip](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)
[![CRAN](http://www.r-pkg.org/badges/version/workers)](http://cran.r-project.org/package=workers)
[![downloads](http://cranlogs.r-pkg.org/badges/workers)](http://cran.rstudio.com/package=workers)
[![Travis build status](https://travis-ci.org/wlandau/workers.svg?branch=master)](https://travis-ci.org/wlandau/workers)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/wlandau/workers?branch=master&svg=true)](https://ci.appveyor.com/project/wlandau/workers)
[![Codecov](https://codecov.io/github/wlandau/workers/coverage.svg?branch=master)](https://codecov.io/github/wlandau/workers?branch=master)


# Teams of Persistent Workers in R

The `workers` package is a job scheduler for R. It launches groups coordinated of workers, and the workers run your jobs in the correct order.

# Installation

`Workers` is a work in progress, and it is currently only available from GitHub.

```{r install, eval = FALSE}
devtools::install_github("wlandau/workers")
```

# Usage

Your workload is a collection of commands named with job IDs.

```{r workload, message = FALSE}
library(workers)
workload <- example_workload()
workload

workload$command[1:2]
```

Some jobs depend the output from other jobs, so `workers` needs a schedule of job IDs.

```{r schedule}
schedule <- example_schedule()
schedule
```

To run your work, just hire a team of persistent workers. 

```{r hire, eval = FALSE}
hire(
  workload = workload,
  schedule = schedule,
  fun = parallel::mclapply,      # for Windows users, parallel::parLapply
  workers = 2,                   # number of persistent workers
  mc.cores = 2                   # arguments to the `lapply()`-like function
)
```

To deploy your workers to a high-performance computing system such as a [SLURM](https://slurm.schedmd.com/) cluster, use the `future_lapply()` function from the [`future.apply` package](https://github.com/HenrikBengtsson/future.apply) and supply the appropriate [`batchtools`](https://github.com/mllg/batchtools) [template file](https://github.com/mllg/batchtools/tree/master/inst/templates).

```{r hire2, eval = FALSE}
plan(
  batchtools_slurm,
  template = "slurm-simple.tmpl", # You supply this file.
  workers = 4
)
hire(
  workload = workload,
  schedule = schedule,
  fun = future.apply::future_lapply,
  workers = 4
)
```

# Ongoing development

The `workers` package is early in its proof-of-concept phase of development. Ideas and plans are discussed in the [issue tracker](https://github.com/wlandau/workers/issues) and outlined in the  [design specification](https://github.com/wlandau/workers/tree/master/specification).
