---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```


![stability-wip](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)
![stability-experimental](https://img.shields.io/badge/stability-experimental-orange.svg)
![stability-unstable](https://img.shields.io/badge/stability-unstable-yellow.svg) <br>
[![Travis build status](https://travis-ci.org/wlandau/workers.svg?branch=master)](https://travis-ci.org/wlandau/workers)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github//wlandau/workers/?branch=master&svg=true)](https://ci.appveyor.com/project/wlandau/workers)
[![Codecov](https://codecov.io/github/wlandau/workers/coverage.svg?branch=master)](https://codecov.io/github/wlandau/workers?branch=master)
[![CRAN](http://www.r-pkg.org/badges/version/workers)](http://cran.r-project.org/package=workers) [![downloads](http://cranlogs.r-pkg.org/badges/workers)](http://cran.rstudio.com/package=workers)


# Workers for R

The `workers` package is a job scheduler for R. It launches groups coordinated of workers do a bunch of jobs together. Some jobs may need to finish before others start, and the workers know how to handle it.

# Installation

`Crew` is a work in progress, and it is currently only available from GitHub.

```{r install, eval = FALSE}
devtools::install_github("wlandau/workers")
```

# Usage

Your workload is a collection of commands named with job IDs.

```{r workload, message = FALSE}
library(workers)
workload <- example_workload()
workload

workload$command[1:2]
```

Some jobs depend the output from other jobs, so `workers` needs a schedule of job IDs.

```{r schedule}
schedule <- example_schedule()
schedule
```

To run your work, just hire a crew of persistent workers.

```{r hire, eval = FALSE}
hire(
  workload = workload,
  schedule = schedule,
  fun = parallel::mclapply,      # `lapply()`-like function to launch persistent workers
  workers = 2,                   # number of persistent workers
  mc.cores = 2                   # arguments to the `lapply()`-like function
)
```

# Future development

### Transient workers

Why would we want one transient worker per job? Because the currently-supported persistent workers can time out. In other words, your computing cluster may impose time limits on long-running workers spawned by `hire(..., fun = future.apply::future_lapply)`.

### Semi-transient workers

It takes a lot of overhead to launch a transient worker for every single job. We will eventually want to distribute groups of jobs among the workers using one of the [knapsack problems](https://en.wikipedia.org/wiki/List_of_knapsack_problems).
